---
title: "Week 1 Exercise (part b)"
author: "Anthony Sonrel"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

*Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. (In general, do not just dump the R code and plots in the HTML document; break your exercises into sections with headings, add some text and make it readable.*



## Sample from a log-normal distribution

Set up seed for reproducibility:
 
```{r params}

rseed = 1

```

Create and store values form log-normal distribution: 

```{r lognorm}

set.seed(rseed)
lognorm <- rlnorm(100, 1, .25)

```


## Plot

Distribution of the log-normal distribution: 

```{r}

par(mfrow = c(1,2))
hist(lognorm, breaks = 20, main = "log-normal distribution")
hist(log(lognorm), breaks = 20, main = "log-normal distribution\n(log-scale)")

```

The sample has a **mean** of `r round(mean(lognorm), 2)` and a **variance** of `r round(var(lognorm), 2)`. 


## Session info

```{r}

sessionInfo()

```

